Full text search hack with Shiny/R

### 2015-12-25 article.rmd
data table output working

---
title: "article"
author: "Emanuel Calvo"
date: "December 22, 2015"
output: html_document
runtime: shiny
---

```{r init, message = FALSE, echo=FALSE}
library(shiny)
require(RMySQL)
library(ggplot2)

@@

@@

@@

Following stats are from the bookContent table (which has an average length of `r rs$len` characters )

@@

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r, echo=TRUE}
        ui <- shinyUI(fluidPage(
                mainPanel(textInput("filtering", "FTS Filter:", ""),
                          submitButton("Stats!"),
                          #plotOutput("plot")
                          uiOutput('table')
                          )
        ))
        server <- function(input, output, session) {
                output$plot<-renderPlot({
                        f<-function(x) {as.character(input$filtering)}

                        sql <- paste("SELECT sourceTable, 
        sum(scoreBoolean) as sumBoolean, 
        sum(scoreQE) as sumQE,
        max(scoreBoolean) as maxBoolean,
        max(scoreQE) as maxBoolean,
        avg(scoreBoolean) as avgBoolean, 
        avg(scoreQE) as avgQE,
        avg(lengthContent) avgLength,
        avg(scoreQE) / count(sourceTable) as weight,
        count(sourceTable) as countOccurrences
FROM
(
SELECT \"BC\" as sourceTable, FTS_DOC_ID, match(BC.content) against (\"" ,f(x) ," \" IN BOOLEAN MODE) as scoreBoolean,
       match(BC.content) against (\""  ,f(x), "\" IN NATURAL LANGUAGE MODE WITH QUERY EXPANSION) scoreQE,
       length(content) as lengthContent
FROM
        bookContent BC
WHERE
  match(BC.content) against (\"" ,f(x)," \" IN NATURAL LANGUAGE MODE WITH QUERY EXPANSION)
UNION
SELECT \"BL\" as sourceTable, FTS_DOC_ID, match(BL.content) against (\"",f(x)," \" IN BOOLEAN MODE) as scoreBoolean,
       match(BL.content) against (\"" ,f(x)," \" IN NATURAL LANGUAGE MODE WITH QUERY EXPANSION) scoreQE,
       length(content) as lengthContent
FROM
        bookContentByLine BL
WHERE
  match(BL.content) against (\"", f(x) ,"\" IN NATURAL LANGUAGE MODE WITH QUERY EXPANSION)
) unionTable
GROUP BY sourceTable
;" , sep = "")
                        rs <- dbGetQuery(con, sql)
                        #rs
                        #x<-1:10

                        output$table <- renderTable({
                            if (is.null(Data())) {return()}
                            print(Data()$rs)
                          }, 'include.rownames' = FALSE
                           , 'include.colnames' = TRUE
                           , 'sanitize.text.function' = function(x){x}
                        )

                        #pairs(rs$sourceTable + rs$weight, data = rs)
                        #pairs(rs[,2:10])
                        # plot(x,f(x))
                }                        
                )              
        }

shinyApp(ui = ui, server = server)
```

>>>>

---
title: "Full text search hack with Shiny/R"
author: "Emanuel Calvo"
date: "December 22, 2015"
output: html_document
runtime: shiny
---

```{r init, message = FALSE, echo=FALSE}
options(width = 9999)
knitr::opts_chunk$set(width=9999)

library(knitr)
library(shiny)
require(RMySQL)
library(ggplot2)

@@

The point of this article will be clarify when each algorithm fits in each situation.

@@

As we can observ on the previous examples, the query extension algorithm has some noisy produced by the double query
generated in order to join  the results.

@@

Following stats are from the bookContent table (which has an average length of `r rs$len` characters ).

@@

The following form will allow you to search across the stats over the tables
of the filtering provided dynamically.

Keep in mind that the numbers are not meaningful as we can't compare rankings
between `query extension` and `boolean`.

```{r, echo=FALSE}
        ui <- shinyUI(fluidPage(
                mainPanel(textInput("filtering", "FTS Filter:", "default"),
                          submitButton("Stats!"),
                          uiOutput('table')
                          )
        ))

        server <- function(input, output, session) {

                Data = reactive({
                  f<-function(x) {as.character(input$filtering)}

                      sql <- paste("SELECT sourceTable, 
                                      sum(scoreBoolean) as sumBoolean, 
                                      sum(scoreQE) as sumQE,
                                      max(scoreBoolean) as maxBoolean,
                                      max(scoreQE) as maxBoolean,
                                      avg(scoreBoolean) as avgBoolean, 
                                      avg(scoreQE) as avgQE,
                                      avg(lengthContent) avgLength,
                                      avg(scoreQE) / count(sourceTable) as weight,
                                      count(sourceTable) as countOccurrences
                              FROM
                              (
                              SELECT \"byParagraph\" as sourceTable, 
                                    FTS_DOC_ID, match(BC.content) against (\"" ,f(x) ," \" IN BOOLEAN MODE) as scoreBoolean,
                                     match(BC.content) 
                                        against (\""  ,f(x), "\" IN NATURAL LANGUAGE MODE WITH QUERY EXPANSION) scoreQE,
                                     length(content) as lengthContent
                              FROM    bookContent BC
                              WHERE
                                match(BC.content) against (\"" ,f(x)," \" IN NATURAL LANGUAGE MODE WITH QUERY EXPANSION)
                              UNION
                              SELECT \"byLine\" as sourceTable, 
                                      FTS_DOC_ID, match(BL.content) against (\"",f(x)," \" IN BOOLEAN MODE) as scoreBoolean,
                                     match(BL.content) 
                                      against (\"" ,f(x)," \" IN NATURAL LANGUAGE MODE WITH QUERY EXPANSION) scoreQE,
                                     length(content) as lengthContent
                              FROM
                                      bookContentByLine BL
                              WHERE
                                match(BL.content) against (\"", f(x) ,"\" IN NATURAL LANGUAGE MODE WITH QUERY EXPANSION)
                              ) unionTable
                              GROUP BY sourceTable
                              ;" , sep = "")

                      rs <- dbGetQuery(con, sql)
                      return(rs)

                })

                        output$table <- renderTable({Data()})

        }

shinyApp(ui = ui, server = server)
